\section*{Index of Abbreviations}
\addcontentsline{toc}{section}{Index of Abbreviations}
\begin{longtable}{@{}p{.275\textwidth}@{}p{.725\textwidth}@{}}
    app & Application\\
    app user & the intended audience for the app\\
    CDN & Content Delivery Network. Supports high availability and performance for static content on the internet. \\
    CSS & Cascading Style Sheets. A language used to style web pages \\
    DNS & Domain Name System. Used to translate domain names into IP-Addresses \\
    eHealth & "a paradigm involving the concepts of health, technology, and commerce, with commerce and technology as tools in the service of health"\footnote{\cite{MartinezPerez.2013}, p. 2}. Belonging to the field of telehealth.\footnote{cf. \cite{MartinezPerez.2013}, p. 2}\\
    ePill & a patient-centered health IT service which offers information on pharmaceuticals and aggregation of data in context\\
    framework & can contain source code, tools and libraries, which together provide specific or common but abstracted functionality\\
    frontend & visible user interface for the app user\\
    HECAT & Health Education Curriculum Analysis Tool\footnote{\url{http://www.cdc.gov/HealthyYouth/HECAT/}}\\
    HIT & abbreviation for Health Information Technology\\
    HTML & HyperText Markup Language. A markup language to design web pages. \\
    IDE & abbreviation fro Integrated Development Environment\\
    JSON & JavaScript Object Notation. Represents data structures human-readable \\
    mHealth & "medical and public health practice supported by mobile devices, such as mobile phones, patient monitoring devices, personal digital assistants (PDAs), and other wireless devices"\footnote{\cite{WorldHealthOrganization.2011} cited by \cite{MartinezPerez.2013}, p. 2}. Also known as m-Health\\
    mHealth apps & "aim at providing seamless, global access to tailored health IT services and have the potential to alleviate global health burdens"\footnote{\cite{Dehling.2013}, p. 1}\\
    MVC & Model-View-Controller. A software architecture pattern which separates logic and user interfaces. Models are representatives of data structures, views contains the user interface definitions and controllers contain the application's logic\\
    information security & Prevention from unauthorized access to information. In this context especially sensitive, personal information\\
    NDK & Native Development Kit. Bundled software and tools which enabled the developer to implement programs on native-code languages\footnote{cf. \url{http://developer.android.com/tools/sdk/ndk/index.html}}\\
    OS & operating system\\
    SDK & abbreviation for Software Development Kit. Bundled software and tools for developing with or for a specified OS or framework\\
    sensitive information & information, which is personal. Can be related to financial, health or otherwise personal relevant information\footnote{Suggested by \cite{FutureofPrivacyForumCenterforDemocracy&Technology.2011}, p. 6, although the definition varies}\\
    telehealth & delivery of medical- or health-related information or services via telecommunication technologies\\
    usability & "extent to which a product can be used by specified users to achieve specified goals with effectiveness, efficiency and satisfaction in a specified context of use"\footnote{\cite{Yeh.2012}, p. 64 as quoted from ISO 9241-11 (1998)}\\
    use value & the utility of consuming a good or service\\
    user interface & \todo{Defintion!}\\
    W3C & World Wide Web Consortium\footnote{\url{http://www.w3.org}} \\
\end{longtable}